---
title: "Fourier_Transformation"
subtitle: "Based on the 3blue1brown Video"
author: "Steffen Schwerdtfeger"
date: "`r Sys.Date()`"
---

The following is based on the 3blue1brown tutorial on Fourier Transformation.
url{# https://www.youtube.com/watch?v=spUNpyF58BY&t=70s}
There is also a python script that produces equivalent results, however the
python code is not well documented and therefore hard to read for beginners.
You can find the python script based on the same video by 3blue1brown here: 
url{https://github.com/thatSaneKid/fourier/blob/master/Fourier%20Transform%20-%20A%20Visual%20Introduction.ipynb}

The below code also does not use list types, such as the mentioned python script.
The below is a rather direct representation of the mathematical formulas.
The python code uses a list (and in R we could do so too) in order to have
100 times (for 100 winding / sampling frequencies) one position for the real
and one for the imaginary part. In R this can be extracted from the result
of rather directly typing in the formula using Im() and Re() to extract the
imaginary and real part for plotting. However, this is only necessary in R
using ggplot. The basic plot() function can handle the full complex number
by itself via automatically applying Im() and Re(), so only one input,
$g_t*exp(-2*pi*i*samp_f[i]*t)$, where $g_t = cos(2*pi*freq*t)$, is needed
for the wound up version of the cos() wave. However, at first it did not work to plot
multiple plots via a for loop using plot() since it kind of messed up 
the plot options which required to clear environment... THE REASON was simple 
but fatal: I have named the index variable in the loop "i", even though i is 
set below as a constant imaginary number... This mistakes messes up your environment!


```{r}
# Load libraries:
#install.packages("gridExtra")
library(gridExtra) # for grid.arrange()
#install.packages("ggplot2") # or tidyverse
library(ggplot2)   # for ggplot()


# Define the time as a frequency with a certain precision of points (by=):
time = seq(0,1,by=.0001) # This sets Hz as unit of frequency

# Define wave frequency 
freq = 3 # == 3 Hz

# Winding / sampling frequency
samp_f = seq(0,10, by = .1) # from zero to 10 in steps of .1
length(samp_f) # length 101, so we will only plot up to 9.9 Hz winding freq (same in the python script)

# Set complex number:
i = complex(real = 0, imaginary = 1) # beware to NOT USE "i" as index variable in a for loop from now on!!

# Cos wave Definition. cos() for all time multiplied by frequency of the cos() wave and 2*pi 
# for radians period, i.e. normalized time in unit of Hz. 

# This cosine wave is used in the python script creates a circle when samp_f == freq:
# g_t = cos(2*pi*freq*time) 

# This cosine wave is used in the 3blue1brown video, shifted upwards, 
# creates dented circle at samp_f == freq
g_t = cos(2*pi*freq*time) + 1 

# More than one frequency
#freq1 = 3; freq2 = 6
#amp1 = 1 ; amp2 = 1
#g_t = amp1*cos(2*pi*freq1*time) + amp1*cos(2*pi*freq2*time) 

# Plot cosine wave:
plot(x = time, y = g_t, type = "l", xlab = "Time in Seconds", 
                                    ylab = "g_t = cos(2*pi*freq*time)", 
                                    col = "deepskyblue3")


```

# Wound up cosine wave with different winding / sampling frequencies

```{r , fig.asp = 15, fig.width = 8}
# Plot all 101 plots. Use the arrows to mimic a gif of the transition, using different sampling 
# frequencies. Using for loop for the plotting:

# Initialize list for storing plots (used for Rmarkdown version):
plots = list()

# Min max of each Re and Im for flexible plotting routines (limiting the y- and x-axis of a plot):
min_max = matrix(0, ncol = 4, nrow = length(samp_f))
for(index in 1:length(samp_f)){
  min_max[index,1] = min(Re(g_t*exp(-2*pi*i*samp_f[index]*time)))
  min_max[index,2] = min(Im(g_t*exp(-2*pi*i*samp_f[index]*time)))
  min_max[index,3] = max(Re(g_t*exp(-2*pi*i*samp_f[index]*time)))
  min_max[index,4] = max(Im(g_t*exp(-2*pi*i*samp_f[index]*time)))
} # End for index

# Matrix for all the means of g_hat for Re and Im:
g_hat_mean = matrix(0, ncol = 2, nrow = length(samp_f))
  
# Mean of Re and Im for plot of the center of mass further below
for(index in 1:length(samp_f)){
  g_hat_mean[index,1] = Re(mean(g_t*exp(-2*pi*i*samp_f[index]*time)))
  g_hat_mean[index,2] = Im(mean(g_t*exp(-2*pi*i*samp_f[index]*time)))
} # End for index

# Turn into data.frame:
g_hat_mean_df = as.data.frame(g_hat_mean)
colnames(g_hat_mean_df) = c("Re","Im")

# Set up list, otherwise plotting is not possible using ggplot via a loop:
plots = list()

for(index in 1:length(samp_f)){ # don't call index "i" when "i" was defined 
                                # above as a constant variable!!!
  # Create data frame with coordinates of wound up function for respective samp_f[index]:
  data = as.data.frame(cbind(Re(g_t*exp(-2*pi*i*samp_f[index]*time)), 
                             Im(g_t*exp(-2*pi*i*samp_f[index]*time))))
  
  # Adjust colnames:
  colnames(data) = c("Re","Im")
  
  # Extract coordinates for point of central mass:
  point = g_hat_mean_df[index,]
  
  # Plot via ggplot:
  plots[[index]] =  ggplot(data, aes(x = Re, y = Im)) +
    geom_path(color = "darkorchid4") +  # Color for line of the plot
    geom_point(data = point, aes(x = Re, y = Im), # add point of central mass
               color = "darkblue", size = 3) +  # color and size of the point
    labs(title = paste("Sample Frequency", samp_f[index], "Hz"), 
         x = "Real Number", y = "Imaginary Number") +
    xlim(c(min(min_max[,1]),max(min_max[,3]))) +  # making sure that plot is not out of bounds
    ylim(c(min(min_max[,2]),max(min_max[,4]))) +  # and not just centralized
    theme(aspect.ratio = 1,plot.title = element_text(size=5), 
          plot.margin = margin(t = 10, r = 10, b = 10, l = 10, unit = "pt"))+ 
    coord_fixed(ratio = 1)+
    theme_minimal()# white instead of grey background
     
    
} # End for index

# Plot grid of plots:
grid.arrange(grobs = plots, ncol = 3)

```

# Plot Re and Im of the center of mass function g_hat(samp_f)

```{r}
# Matrix for all the means of g_hat for Re and Im:
  g_hat_mean = matrix(0, ncol = 2, nrow = length(samp_f))
  
  # Mean of Re and Im for plot of the center of mass further below
  for(index in 1:length(samp_f)){
    g_hat_mean[index,1] = Re(mean(g_t*exp(-2*pi*i*samp_f[index]*time)))
    g_hat_mean[index,2] = Im(mean(g_t*exp(-2*pi*i*samp_f[index]*time)))
  } # End for index
  
  # Function of the center of mass of the wound up graph, peaking at the 
  # frequency or frequencies of the initial cosine wave!
  plot(x = samp_f, y = g_hat_mean[,1], type ="l",   # plot of mean(Re)
       xlab = "Winding Frequency",  # rename labels
       ylab = "Mean of g_hat(f)",
       main = "Function of the Center of Mass for each Winding Frequency",
       col = "deepskyblue3", ylim = c(min(min(g_hat_mean[,1]),min(g_hat_mean[,2])), 
                                      max(max(g_hat_mean[,1]),max(g_hat_mean[,2]))))
  lines(x = samp_f, y = g_hat_mean[,2], type = "l", col = "hotpink2") # Add mean(Im) to plot
  axis(1, at = seq(min(samp_f),max(samp_f), by = 1)) # Adjust x-axis tick mark (every integer step)
  legend("bottomright",legend = c("Re","Im"),               # add legend
         col = c("deepskyblue3","hotpink2"),  # legend line color
         lty = 1,   # line type of legend (corresponding to plot)
         cex = .75) # size of legend in ratio to standard size
  
```





