---
title: "Universal SoSci-Survey Analysis Script" 
subtitle: "for CIPom / LERNZENTRUM @ Charité" 
author: "Steffen Schwerdtfeger - CIMPOM/LZ Tutor and JNOS Editor"
date: "`r Sys.Date()`\\clearpage"  # add \\clearpage so that TOC is on the next page!
output:                            # \pagebreak below is for after the TOC, Sys.Date() = System Date
  pdf_document:   # Adjustment of output options:
    toc: TRUE       # content table with page number for each chapter
    toc_depth: 3    # depth means up to 1.1.1 (= 3), 
                    # this script actually only uses one level...
    latex_engine: xelatex  # makes sure é is correctly shown 
                           # in markdown texts (no problem in titles somehow)
header-includes: # The below makes sure that page numbering starts at page 2.
                 # The below took me ages to figure out, even with AI, which I avoid, no success.
                 # Why? The issue was, that I was unaware of the fact that the tab
                 # spacing in this YAML code has a syntactic meaning, such that if header-includes:
                 # is tabbed, it will not be read properly!! AI also offered "bloated code" 
                 # with options I didn't even chose and was therefore very confusing to read... 
                 # I eventually figured it out via regular websites... Here it is, one line: 
  - \thispagestyle{empty}   # Remove header and the footer including numbering from title page
word_document: default      # no options for potential word output are set (but are possible)
editor_options: 
 markdown:
    wrap: 72 # Line length of 72 characters; ensured for the case of multiple editors
---

``` {r, echo = FALSE, warning = FALSE, message = FALSE}
# echo = FALSE, warning = FALSE, message = FALSE => makes sure console output, error messages
# and warnings are not knitted into the pdf...

#############################
#############################
# EXPORT AND IMPORT OPTION: # 
#############################
#############################

# Set your Path including file name and file ending! 
# CHANGE DATA AND CODE FILE TO CSV FORMAT FIRST!!!
# INPUT SCHEME: path = "YOUR_PATH_INCLUDING_FILENAME.csv" 
# NOTE: change \ to / in path in Windows!!!!
path_data = "data_Example.csv" # here abbreviated, since I set up R project with set wd()...
path_code = "codebook_Example.csv" # ... same here.


# EXPORT PATH Default FALSE for no .csv export
export_text = FALSE
export_path = "text_response_Example.csv"

# NO ADJUSTMENT NEEDED HERE! NO ADJUSTMENT NEEDED HERE! NO ADJUSTMENT NEEDED HERE!
# This is ust the actual code fot the import of CSV (did not work well with the .xlsx Versions...):
data = read.csv(path_data)
code = read.csv(path_code)
Frequency = c(0) # used to create an empty "Frequency" column, with 0 as default value...
code = cbind(code,Frequency) # ... via this line (fills up the whole column with 0 eventually).

################
################
# PLOT OPTIONS #
################
################

# Plot options, default is plot all (note bar and hist are the same, just different functions; 
# a histogram is actually a bar plot with y-axis entailing densities, here it is frequency and
# percentage...)

# POSSIBLE OPTIONS => default is all three: options = c("box","heat","bar") 
options = c("box","heat","bar")

```

\pagebreak

# Details on Statistics, Data Visualisation, Handling of Text Responses and the Rmarkdown Script

**Statistics below entails:** \newline Only for data that is tagged
nominal in the codebook (likert scale data).\newline a)
quantiles\newline b) median\newline c) mean\newline d) sd\newline e)
frequency of NA's (no response cases)\newline

**Plot types:**\newline Depending on chosen options, a bar plot, heat plot 
and/or box plot can be chosen -- for nominal data. Default option is all three.
See first code chunk to adjust plot options. For dichotomous / Boolean data 
only bar plots are provided. \newline

**Free Text Responses**\newline The corresponding Rmarkdown optionally
allows for an export of all the free text answers as .csv table, when a
parameter is set TRUE in the first code chunk (default is FALSE; see
very last code chunk for respective code, e.g. to add .xlsx as export
option).\newline However, the PDF Export comes with a table as well:
three columns, one with the question label, one for the index of each
element for each question (not mere row number of the exported table)
and one column with the free text answers.\newline

## What does the corresponding Rmarkdown script do and how can I make use of it?

The Rmarkdown script corresponding to this PDF is a generalized way to
process reoccurring survey data with repeating data table and code book
structure (e.g. via SoSci Survey in this case). You start with defining your 
file path for the code book and the data table in the first code chunk (i.e., 
demarcated space within the Rmarkdown script, where code can be executed). 
The supported import format is CSV (which is recommended; the R function 
read.csv() for regular comma delimiter tables is used). In the same first code 
chunk, you can optionally export a CSV with the free text responses by setting
the respective parameter from FALSE (default) to TRUE. For the text export and 
table included in the PDF, the columns STATUS, SERIAL, REF, QUESTNNR, MODE were
excluded (not entailed in the example code book anyways, but for regular SoSci
Survey code books). The layout is kept simple and it was made sure that page 
numbering starts at page 2 (which took quite a while to figure out, since I 
wasn't aware of the fact that tab spacing or spacing in the YAML code has a 
syntactic meaning; keep that in mind when further adjusting this script).

\par

The script is universal in the sense that the specific variable names of
the question do not matter, the amount of questions and the possible
options (likert scale or not) etc. do not matter... Important is that
the data table has to have a certain structure, were each
question/field, i.e., the responses (answers) to each variable
(question), has to to have its own column (not row, or any other format,
such as a list() object formats in R). Take a look at the example data table 
to get a better understanding of their scheme. Apart from that, the code book 
also has to have the same table structure as in this example. More important
-- and the biggest constrain of this Rmarkdown script -- is the fact that it 
also has to follow the scheme of the column names and the options for the 
data types as given in this example (SoScie Surcey code book structure). This 
essentially concerns the following column names of the code book: Variable, 
Variable.Label, Response.Label, Response.Code, Variable.Type and the added 
dummy column Frequency for later processes (R is case sensitive, therefore the 
capital letters).\newline The below script processes data of the variable 
types BOOL, DICHOTOMOUS (both essentially binary), TEXT (free text response) 
and NOMINAL (likert scale data).

\par

Any kind of text data is pre-processed such that faulty uni-code
transformation of "Umlaute" and "ß" are corrected in the columns
Variable.Label and Response.Label of the code book, as well as in the
respective free text response columns of the data table. As mentioned in
the previous chapter, a table is added to the PDF using the package
kableExtra.

\par

For the calculation of the quantiles, median, mean, sd and NA
frequencies the regular summary() function is used in the Rmarkdown
script. For the summary (median, mean, quantiles) the variable labels Consent,
Geschlecht, Alter, and Studiengang were omitted too (Engl. age, sex, course 
of study). CAVE: The variable label Alter is actually "Alter " in the data table, 
and yes, it has an unnecessary spacing in the column name, the code below also 
filters for case without spacing; this problem can occur at least, if you want 
to filter for "Alter " via the logical operator "==" in R. I could have used
grep(), however the word "Alter" can appear in other words as well, so I
would not recommend. 

\par

The bar plots entail two y-axes, left and right: frequencies and
percentages -- note that given an example with around $n = 100$ is confusing, 
since when the sample size is around $100$, it leads to a case where the numeric 
tick marks of both y-axes are (nearly) the same, since frequency is equivalent 
to percentage (given a sum of frequencies of $n = 100$). This was the case with
the original data for this script, and yes, it was confusing.\newline 
The x-axis labels of bar plots were tilted, so they cannot overlap in the plot
horizontally in case the likert scale options consists of a longer word
or phrase.\newline 
For the bar plots, the variable "STATUS" was omitted, since
it had a total frequency of zero (this may casually be the case).
Note that columns with zero sum of frequencies are a problem for the bar
plot (ggplot2) since they globally mess up the y-axis numeric tick marks
of the percentage axis for any plot -- they disappear as soon as a
zero sum of frequencies case is plotted. The code for this
script automatically omits zero sum of frequencies
variable responses to avoid this of happening. The heat map should be 
self-explanatory, however, it was necessary to reverse / mirror the labels in 
order to be able to flip the y-axis. This was due to the fact, that the 
frequency heat map legend was mostly inverted to the most outcomes, where the 
highest frequency is shown on the top. The box plot is also straight forward, 
except of the fact that missing responses where excluded. 

\par

More information on the plotting routines and such can be found in the
actual Rmarkdown script this PDF was "knitted" from (as it's said). The
script was heavily commented and there is also a thorough tutorial on
the script provided in the respective JNOS Stat-o-Sphere R-Basic
tutorial article, corresponding to the CIPOM/LZ \@ Charité in-person
peer-teaching tutorial series.
\url{https://doi.org/10.56776/abbd964d.665f7de5}


```{r, echo = FALSE, warning = FALSE, message = FALSE}

#############
#############
# Libraries #
#############
#############

###### The below loads packages 
# install.packages("tidyverse")
library("tidyverse") # filter() and ggplot()
#install.packages("stringi")
library("stringi") # for changing faulty umlaut and ß conversion
#install.packages("kableExtra")
library("kableExtra") # for kbl() text response table and summary table
#install.packages("gridExtra")
library("gridExtra") # needed for grid.arrange() for multiple plots on a page without looking messy


#############################################
#############################################
# Pre-Processing Faulty Unicode Translation #
#############################################
#############################################

# Correct Umlaut in code table, column response label:
for(i in 1:length(code$Response.Label)){
  code$Response.Label = stri_replace_all_fixed(
    code$Response.Label, # Col that is targeted
    c("\xc4","\xe4","\xdc","\xfc","\xd6","\xf6","\xdf"), # exchange to...
    c(  "Ä",   "ä",  "Ü",   "ü",    "Ö",  "ö",   "ß"),   # ... this
    vectorize_all = FALSE)
} # End for i

# Same for Variable.Label 
for(i in 1:length(code$Variable.Label)){
  code$Variable.Label = stri_replace_all_fixed(
    code$Variable.Label, # Col that is targeted
    c("\xc4","\xe4","\xdc","\xfc","\xd6","\xf6","\xdf"),  # exchange to...
    c(  "Ä",   "ä",  "Ü",    "ü",   "Ö",  "ö",   "ß"),    # ... this.
    vectorize_all = FALSE)
} # End for i


```

\pagebreak

# Basic Statistical Analysis - Quantiles, Median, Mean, SD and Frequency of NA's

Note that the NA's (not assigned) stand for cases with no response.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
#########################################################
#########################################################
# Summary() - Quantiles, Median, Mean) for Nominal Data #
#########################################################
#########################################################

# Filter all Nominal Code (likert scale data):
nominal = filter(code, Variable.Type == "NOMINAL")

# Our goal is now to get a table where the result of each column is put in
# a table with the result of each column in one row.

# First we will put all response codes col wise into a table
uniq_ques = unique(nominal$Variable)

# Empty result vector (here no matrix needed...):
nom_sum = c()

# Loop over individual question IDs and cbind() them:
for(i in 1:length(uniq_ques)){
  nom_sum = cbind(nom_sum, data[,uniq_ques[i]])
} # End for i

# Change to format data frame and use first col as colnames
nom_sum_fin = as.data.frame(nom_sum[-1,], header = TRUE)
colnames(nom_sum_fin) = nom_sum[1,]

# Create an empty matrix that has the col length of summary_res[,1] = 6 
# and a row for every question, i.e. the length(results[1,]) = number of questions:
results_table = matrix(0, ncol = length(summary(as.numeric(nom_sum_fin[,1]))),
                          nrow = length(nom_sum_fin[1,]))

# We now use a loop to put the summary of every column together
# We have to use the summary() function again for each column,
# since I could not find a way to reformat the above object summary() objects...:
for(i in 1:length(nom_sum_fin[1,])){             # loop over columns
  results_table[i,] = summary(as.numeric(nom_sum_fin[,i]))   # Calculate summary of 
                                                             # each column (only way it worked)
} # End for i                                # ... and put result in row of results_table[i,]

# Add columnn with Variables of the questions
results_table = as.data.frame(results_table)
results_table = cbind(colnames(nom_sum_fin),results_table)

# Change columns of this table to entail c("Min.", "1st Qu.", "Median", "Mean", "3rd Qu.", "Max.")
# as column names (extract from summary() output of a single column):
colnames(results_table) = c("Question",names(summary(as.numeric(nom_sum_fin[,1]))))

# Round Mean for better table overview:
results_table$Mean = round(results_table$Mean,2) # round mean value

# You may also want to add the SD of every question as well:
SD = c() # Empty vector for results:
for(i in 1:length(nom_sum_fin[1,])){
  extract_col = as.numeric(nom_sum_fin[,i])
  col_no_na = extract_col[!is.na(extract_col)] # get rid of NA's
  SD[i] = round(sd(as.numeric(col_no_na)),2) # get SD and round result
} # End for i

# Final table:
results_table = cbind(results_table,SD) # add sd to result_table
results_table_fin  = results_table[,c(1:5,9,6:8)] # put sd col next to mean

# Delete c("Consent","Geschlecht","Alter","Studiengang"), since they make little
# sense for a summary (Engl. Consent, Sex, Course of study):
# NOT NECESSARY FOR EXAMPLE DATA SET AND CODE BOOK, but for the actual survey 
# this Rmarkdown was made for:
del_rows = c("Consent","Geschlecht","Alter ","Alter","Studiengang")
for(i in 1:length(del_rows)){
  results_table_fin = filter(results_table_fin, Question != del_rows[i])
} # End for i

####### Create a nice table for export:
# Plot as nice looking table
results_table_fin %>%
  kbl(format="latex", booktabs = TRUE) %>% # Booktabs for certain style of that package
  kable_styling(latex_options = c("hold_position", "striped")) # hold_position, otherwise floating object
                                                               # creating funky effects in pdf.

# NOTE THAT THE TABLE WILL ONLY BE SHOWN IN THE PDF OUTPUT OR WHEN YOU EXECUTE CODE IN
# A REGULAR R SCRIPT PARALLEL TO SEE HOW IT LOOKS!!! DON'T GET CONFUSED!!!

# NOTE THAT THE TABLE WILL ONLY BE SHOWN IN THE PDF OUTPUT OR WHEN YOU EXECUTE CODE IN
# A REGULAR R SCRIPT PARALLEL TO SEE HOW IT LOOKS!!! DON'T GET CONFUSED!!!

```

\pagebreak

# Plot for the Analysis of Likert Scale Responses (Bar Plot, Box Plot and Heat Map Possible)

Depending on the chosen options, the below will entail all three possible 
plot types, a combination of two of the three, or only one type of plot (see 
first code chunk to toggle options; default option is all three plot types). 
The bar plot entails frequencies and percentages. Note that in the case of 
the example data for this script, the sample size turns out to be near 100, 
such that the numeric tick marks for percentages and frequencies are nearly on 
the same level. The box plots do not entail missing responses.  

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.align="center", out.width="85%",out.height="85%", fig.pos="hold", fig.asp = 1.5}
# Concerning the above parameters, I am not sure if fig.align="center" and fig.pos)"hold" are necessary
# given different code below. You may experience it yourself, but at some point, for now I may say:
# never change a running system :D You may play around with it yourself. For the context of tutorials I 
# think it is good that they are there to be shown.


###################################################################################################
###################################################################################################
## Extract Frequencies from Data for Heat map, Bar Chart / Histogram and Box plot of Nominal Data #
###################################################################################################
###################################################################################################

# BAR CHART and HISTOGRAM more or less the same, since the hist() function also allows for frequencies
# not densities in the y-axis

# Filter all Nominal Code (likert scale data):
nominal = filter(code, Variable.Type == "NOMINAL")

# Different to the codebook, the imported data does not entail -9 for nicht beantwortet, 
# but "", i.e., empty fields... In order to relate the code to the actual text response,
# we have to change the codebook first:
for(i in 1:length(nominal$Response.Code)){
  if(nominal$Response.Code[i] == -9){   # change -9 in the codebook...
    nominal$Response.Code[i] = ""       # ... to ""
  } # End if
} # End for i
  
# All unique Survey Question IDs: 
ques_id = unique(nominal$Variable)

# Put all Questions into a separate list element each using filter() and
# looping over the vector ques_id with individual nominal 
# likert scale survey question ids:
freq_list = list()
for(i in 1:length(ques_id)){
  freq_list[[i]] = filter(code, Variable == ques_id[i])
} # End for i

# Calculate Frequency and add to freq_list using length(which()) for each response variable:
for(i in 1:length(freq_list)){
  for (j in 1:length(freq_list[[1]][,1])){
    data_col = which(colnames(data) == freq_list[[i]][1,"Variable"]) # Extract Variable for 
                                                                     # below in which()
    # Calculate frequency using length(which()) and add to table in list()...
    freq_list[[i]][j,"Frequency"] = length(which(data[,data_col] == freq_list[[i]][j,"Response.Code"])) 
  } # End for j
} # End for i

# Delete those tables in the list with sum of frequencies of 0, since they mess up the plot:
# Vector with lines to delete, given sum of frequency == 0: 
freq_del = c()
# Frequencies to check for 0:
freqs = c()
for(i in 1:length(freq_list)){
  if(sum(freq_list[[i]][,"Frequency"]) == 0){
    freq_del[i] = i # Positions with Frequency == 0
    freqs[i] = sum(freq_list[[i]][,"Frequency"])
  } # End if
} # End for i

# Now delete all positions with sum of frequency == 0, since the case of no survey 
# item having frequency 0 can occur, it can lead to an error when executing 
# frequ_list2[-0]... So we only keep, given that there is at least one case of 
# a zero sum of frequencies:   
if(length(which(freqs == 0)) > 0){
  freq_list = freq_list[-freq_del]
} # End if

#############################################################
# Loop to Plot Likert Scale Bar Chart / Heat Map / Box Plot #
#############################################################

# For loop successively plots all of the above plot types:
for(i in 1:length(freq_list)){
  
    # Each table including the frequencies is changed into a data frame:
    likert_scale = as.data.frame(freq_list[[i]])
    likert_rev = as.data.frame(freq_list[[i]])

    # Response as factor (relates text to a set of numeric factors, so it is 
    # easier to switch when a function allows data type factor) In general this 
    # is necessary so that the answers in the bar chart aren't jumbled.
    unfactor_labels = likert_scale$Response.Label # Some functions can't handle factorized columns... 
    likert_scale$Response.Label = factor(likert_scale$Response.Label, 
                                         levels = likert_scale$Response.Label)
    # Needed in order to be able to flip y-axis heat for the heat map:
    likert_rev$Response.Label = factor(likert_scale$Response.Label, 
                                       levels = rev(likert_scale$Response.Label))

    ########### BAR PLOT
    ####################
    if(length(grep("bar",options)) > 0){ 
        # Get sum frequency for transformation for second y-axis
        sum_freq = sum(freq_list[[i]][,"Frequency"]) # Sum of freq object; 
                                                     # calling trans = ~./ max() => leads to error!
        #### Bar Chart Plot (same as hist() but via ggplot and more simple in use):
        bar = ggplot(freq_list[[i]]) +
          geom_bar(aes(x=likert_scale$Response.Label, y=Frequency), # Axis labels
                   stat="identity", # frequencies on y-axis
                   fill="skyblue",  # color bars
                   alpha=0.7)+      # opacity of plot
          scale_y_continuous(
          name = "Frequency", # Label of the left side y-axis 
                              # (original y-axis; redundant since aes() already...)
          sec.axis = sec_axis(trans = ~./sum_freq*100,  # transform into percentages
                          name = "Percentage")) +       # label for 2nd y-axis, right side
          ggtitle(freq_list[[i]][1,"Variable.Label"]) + # Title is Question name 
                                                        # (called Variable label in the code book)
          xlab("") + # blank x-label
          coord_fixed(ratio = .4) + # to avoid unusual spacing between plots: 
                                    # set the aspect ratio here and in theme()
          # Below labels with angle for better readability; margin 
          # shrinks the plots, such that 3 fit on a page:
          theme(axis.text.x = element_text(vjust=0.6,angle=20),
                plot.margin = margin(10, 10, 10,10), 
                aspect.ratio = .4) # Here and in coord_fixed(), otherwise plot arrangement messy  
    } # End if length(grep("bar",options)) > 0
  
    ########### Heat Map
    ####################
    if(length(grep("heat",options)) > 0){
       #### Heat map Plot:
       heat = ggplot(likert_rev, aes(x = "", y = Response.Label, fill = Frequency)) + 
         geom_tile(color = "white") +  # Tiles of the Heat map
         geom_text(aes(label = Frequency), color = "black", size = 5) +  # Labels
         scale_fill_gradient(low = "lightblue", high = "blue") +     # Gradient color scheme
         theme_minimal() + # simple scheme
         labs(title = paste(likert_rev[1,1],likert_rev$Variable.Label),
              x = "",                          # Labels, x is left blank
              y = "Response",             
              fill = "Frequency") +            # Label for legend 
          theme(axis.text.x = element_blank(), # Removes the text from the x-axis, title enough 
               axis.ticks.x = element_blank()) +
        # Keeping plot in bounds such that 3 fit on a page
        theme(plot.margin = margin(10, 10, 10,10), aspect.ratio = 1) # coord_fixed() not necessary here
    } # End if length(grep("heat",options)) > 0
 
    ########### BOX PLOT
    ####################
    if(length(grep("box",options)) > 0){
       # Extract Names of relevant columns:
       box_cols_data = unique(nominal$Variable)
   
       # Nominal cols from data:
       data_nom = data[,paste(box_cols_data[i])]
   
       # Delete first element (== Var Label) and empty entries
       Varlab = data_nom[1] # Var Label for Plot
       data_nom = data_nom[-1] # delete Var Label
       data_nom = data_nom[data_nom!=""] # delete "nicht beantwortet", which == "" 
                                         # (-9 to "" was changed with a loop further above)
       data_box = as.data.frame(as.numeric(data_nom)) # convert to data frame, data_nom is now col_name 
                                                      # (necessary format for ggplot())
       colnames(data_box) = c("data_vec") # rename column such data there is no confusion with 
                                          # the object data_nom within ggplot()
     
       # Actual box plot 
       box = ggplot(data_box, aes(x="", y=data_vec)) + 
         geom_boxplot(fill = "skyblue") + # color of fill   
         labs(title = "", x = Varlab, y = "Responses") +           # title label
         coord_fixed(ratio = 2) + # to delete spacing between plots I had to set the aspect
                                  # ratio here and in theme(), same for bar plot above...
         theme(plot.margin = margin(10, 10, 10,10), aspect.ratio = 2) + # keeping plot in bounds such 
                                                                        # that 3 fit on a page
         # Labels instead of numbers on y-axis: 
         scale_y_continuous(breaks = 1:length(likert_scale$Response.Label), # Steps
                            labels = likert_scale$Response.Label)           # Labels for each step
    } # End if length(grep("box",options)) > 0
    
    # Plot via grid.arrange, otherwise it makes trouble arranging the plots on a page (floaty). 
    # Below grid.arrange setup for the case of every possible plot option. Reason is that   
    # plotting without grid.arrange() and grid.arrange() using a list() didn't work for the pdf export. 
    if(length(options) == 3){
       grid.arrange(bar,heat,box, nrow = length(options), ncol = 1, heights = c(1,.5,1))
    } # End if length(options) == 3 
    
    if(length(options) == 2){
       if(length(grep("bar",options)) > 0 & length(grep("heat",options)) > 0){
          grid.arrange(bar,heat, nrow = 2, ncol = 1, heights = c(1,.5))
       } # End if
       if(length(grep("bar",options)) > 0 & length(grep("box",options)) > 0){
          grid.arrange(bar,box, nrow = 2, ncol = 1, heights = c(1,1))
       } # End if
       if(length(grep("heat",options)) > 0 & length(grep("box",options)) > 0){
         grid.arrange(heat,box, nrow = 2, ncol = 1, heights = c(.5,1))
       } # End if
    } # End if length(options) == 2 
    
    if(length(options) == 1){
       if(length(grep("bar",options))){
         grid.arrange(bar, nrow = 1, ncol = 1, heights = c(1))
       } # End if
       if(length(grep("heat",options))){
         grid.arrange(hear, nrow = 1, ncol = 1, heights = c(1))
       } # End if
       if(length(grep("box",options))){
         grid.arrange(box, nrow = 1, ncol = 1, heights = c(1))
       } # End if
    } # End if length(options) == 1
    
} # End for i


```

\pagebreak

# Bar Plot for the Case of Dichotomous and Boolean Variable Responses

Below just uses simple bar plots of binary responses. If there are field
with zero frequencies, they may mess up the numeric tick marks of the
second percentage y-axes, so any question with a total frequency of zero 
responses. 

```{r, echo = FALSE, warning = FALSE, message = FALSE,fig.align="center", out.width="80%",out.height="80%", fig.pos="hold"}

# BELOW SIMILAR TO PLOT OF LIKERT SCALES:

# Filter all bool and dichotomous code:
dichoto = filter(code, Variable.Type == "DICHOTOMOUS")
bool = filter(code, Variable.Type == "BOOL")

# Add them row-wise them together:
binary = rbind(dichoto,bool)

# Add col for frequencies. Needed for freq_list below when calculating 
# the frequencies of each response case:
freq2 = c(0) 
binary = cbind(binary,freq2)

# All unique Survey Question IDs: 
ques_id2 = unique(binary$Variable)

# Put all Questions into a separate list element each using filter() and
# looping over the vector ques_id with individual binary survey question ids:
freq_list2 = list()
for(i in 1:length(ques_id2)){
  freq_list2[[i]] = filter(code, Variable == ques_id2[i])
} # End for i

# Calculate Frequency and add to freq_list2:
for(i in 1:length(freq_list2)){
  for (j in 1:length(freq_list2[[1]][,1])){
    data_col = which(colnames(data) == freq_list2[[i]][1,"Variable"])
    freq_list2[[i]][j,"Frequency"] = length(which(data[,data_col] == freq_list2[[i]][j,"Response.Code"]))
  } # End for j
} # End for i

# Delete those tables in the list with sum of frequencies of 0, since they mess up the plot:
# Vector with lines to delete, given sum of frequency == 0: 
freq_del = c()
# Frequencies to check for 0:
freqs = c()
for(i in 1:length(freq_list2)){
  if(sum(freq_list2[[i]][,"Frequency"]) == 0){
    freq_del[i] = i 
    freqs[i] = sum(freq_list2[[i]][,"Frequency"])
  } # End if
} # End for i

# Now delete all with sum of frequency == 0, since the case of no survey item having frequency 0
# can occur, it can lead to an error when executing frequ_list2[-0]... So we only delete, given
# that there is at least one case:   
if(length(which(freqs == 0)) > 0){
  freq_list2 = freq_list2[-freq_del]
} # End if

# Get sum frequency for transformation for second y-axis:
sum_freq2 = sum(freq_list2[[i]][,"Frequency"]) # Sum of freq object: Can't be called 
                                               # within trans = ~./ max() => leads to error!
# Plot Histogram:
for(i in 1:length(freq_list2)){
  # Plot Histogram:
  bar2 = ggplot(freq_list2[[i]]) +
    geom_bar(aes(x = freq_list2[[i]][,"Response.Label"], y = freq_list2[[i]][,"Frequency"]), # axis labels
             stat ="identity",  # frequencies
             fill =  "skyblue", # col of bars
             alpha = 0.7) +     # Opacity
    scale_y_continuous(
    name = "Frequency", # Label of the left side y-axis 
                        # (original y-axis; redundant since aes() already...)
    sec.axis = sec_axis(trans = ~./sum_freq2*100,   # transform values into percentages
                        name = "Percentage")) +  # label for 2nd y-axis
  ggtitle(paste(freq_list2[[i]][1,"Variable.Label"]))+
    xlab("") +
    # Labels with angle for better readability
    theme(axis.text.x = element_text(vjust=0.6,angle=20),,plot.margin = margin(60, 60, 60, 0)) 
  # Plot bar (again, needed for ggplot() within a loop...):
  plot(bar2)
  # New pdf page after plotting
} # End for i

```

\pagebreak

# Free Text Answers

Below all free text answers are listed in a table. The first column
entails the numeric index of each answer for one specific question
(variable label in the codebook), i.e., not the mere line index of the
whole table below.\newline Additionally a .csv export can be created of
all the questions that were answered via free text response input,
entailing the respective question or variable label, the index of each
element of responses for each responses (not mere row indices), and the
answer. See very last code chunk regarding text processing in the
Rmarkdown and very first code to adjust the respective parameter to TRUE
for such an export (default is FALSE).

```{r,echo = FALSE, warning = FALSE, message = FALSE}

#######################
# Language Processing #
#######################

### Pre- Processing Text Elements:
text_general = filter(code, Variable.Type == "TEXT")
# Status actually output similar to likert scale therefore plotted with dichotomous and bool:
text = filter(text_general, Variable != "STATUS") # deletes!
# Filter other unnecessary Variables with TEXT as type:
del = c("SERIAL", "REF","QUESTNNR","MODE")
for(i in 1:length(del)){
   text = filter(text, Variable != del[i])
} # End for i

# All unique Survey Question IDs: 
ques_id3 = unique(text$Variable)

# Put all Questions into a separate list element each using filter() and
# looping over the vector ques_id with individual binary survey question ids:
text_list = list()
for(i in 1:length(ques_id3)){
  text_list[[i]] = data[,ques_id3[i]]
  omit_na = text_list[[i]]
  omit_na = omit_na[omit_na!=""]
  omit_na = omit_na[omit_na!="."]
  omit_na = omit_na[omit_na!="/"]
  text_list[[i]] = omit_na[omit_na!=" -"]
} # End for i

# Correct Umlaut in code table, column response label:
for(i in 1:length(text_list)){
  text_list[[i]] = stri_replace_all_fixed(
    text_list[[i]], 
    c("\xc4","\xe4","\xdc", "\xfc","\xd6","\xf6", "\xdf"), # exchange to...
    c(  "Ä",   "ä",  "Ü",    "ü",    "Ö",  "ö", "ß"),   # ... this
    vectorize_all = FALSE)
} # End for i

### Natural Language Processing would be possible, but so far didn't really
### lead to insightful perspectives/results...
### However, below is some code that exports the questions as table.
text_export = c()
for(i in 1:length(text_list)){
     text_ques = as.data.frame(text_list[[i]][1]) # first col as.data.frame for class integrity
     Index = c(1:length(text_list[[i]][-1]))  # col for indices of each question (not the table as such..)
     text_ques_resp = cbind(Index, text_ques,text_list[[i]][-1]) # cbind() them
     text_export = as.data.frame(rbind(text_export,text_ques_resp)) # rbind() with previous lines...
} # End for i

# Change second col name:
colnames(text_export)[2:3] = c("Question","Answers") 

#### Print/Plot Table with Text using kableExtra package: 
text_export %>%
  kable(format="latex", booktabs = TRUE, longtable = TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))%>%
  column_spec(2, width = "3.5cm")%>% # Adjusts column width such that the text within a field
  column_spec(3, width = "9.5cm")%>% # breaks, otherwise specially col Answer gets very wide,
                                     # clipping over and over again... 
  row_spec(seq(1, nrow(text_export), 2), background = "#F0F0F0") 
                                     # striped table for better readability
                                     # kable_styling("striped") does not work somehow, t#
                                     # it worked with latex_options = in the summary table though...

# NOTE THAT THE TABLE WILL ONLY BE SHOWN IN THE PDF OUTPUT OR WHEN YOU EXECUTE CODE IN
# A REGULAR R SCRIPT PARALLEL TO SEE HOW IT LOOKS!!! DON'T GET CONFUSED!!!

# NOTE THAT THE TABLE WILL ONLY BE SHOWN IN THE PDF OUTPUT OR WHEN YOU EXECUTE CODE IN
# A REGULAR R SCRIPT PARALLEL TO SEE HOW IT LOOKS!!! DON'T GET CONFUSED!!!


##################
##################
#### Export Text #
##################
##################

if(export_text==TRUE){
  write.csv(text_export,export_path)
} # End if

```
